My title

### 2024-03-12 paper/paper.qmd
Update paper.qmd

#### Read in cleaned data ####
cleaned_data_post_strat <-read_csv(file = here("data/analysis_data/usa_00002_cleaned.csv"), show_col_types = FALSE)
cleaned_data_survey <- read_csv(file = here("data/analysis_data/ns20191003_cleaned.csv"), show_col_types = FALSE)
```

@@

The variables we have decided to use in this analysis from the dataset are 'sex', 'race', 'stateicp', 'age_group', and 'education'. We have filtered out the respondents who have answered 'other' or no available sex data from the raw dataset for simplicity of the analysis. Therefore, 'Sex' is categorized into 'Male' and 'Female'. 'Race' is divided into 'White', 'Black', 'Asian', 'American Indian' and 'other'. As mentioned earlier, the fact that white, black and Asian together make up around 93 percent of the U.S population, this categorization is justified. 'stateicp' is a record of all the states in the U.S. We have used the abbreviations for each state, for example, 'CT' for Connecticut, 'ME' for Maine, 'MA' for Massachusetts. We have the data of 55 states in total. 'age_group' categorized the respondents' age into four groups: '18-29', '30-49', '50-64' and '65+'. 'education' is divided into four categories: 'High school or less', 'Some college', 'College degree', 'Postgrad'. We filtered out those unknowns, and cleaned the dataset by assigning each respondent to the right category accordingly.

```{r}

@@

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

>>>>

#### Read in necessary data and model ####
cleaned_data_post_strat <-read_csv(file = here("data/analysis_data/usa_00002_cleaned.csv"), show_col_types = FALSE)
cleaned_data_survey <- read_csv(file = here("data/analysis_data/ns20191003_cleaned.csv"), show_col_types = FALSE)
survey_model <- readRDS(file = here("models/consider_trump.rds"))
predicton_model <- readRDS(file = here("models/census_data_with_predictions.rds"))
```

@@

The variables we have decided to use in this analysis from the dataset are 'sex', 'race', 'stateicp', 'age_group', and 'educd'. We have filtered out the respondents who have answered 'other' or no available sex data from the raw dataset for simplicity of the analysis. Therefore, 'Sex' is categorized into 'Male' and 'Female'. 'Race' is divided into 'White', 'Black', 'Asian', 'American Indian' and 'Other'. As mentioned earlier, the fact that white, black and Asian together make up around 93 percent of the U.S population, this categorization is justified. 'stateicp' is a record of all the states in the U.S. We have used the abbreviations for each state, for example, 'CT' for Connecticut, 'ME' for Maine, 'MA' for Massachusetts. We have the data of 55 states in total. 'age_group' categorized the respondents' age into four groups: '18-29', '30-49', '50-64' and '65+'. 'education' is divided into four categories: 'High school or less', 'Some college', 'College degree', 'Postgrad'. We filtered out those unknowns, and cleaned the dataset by assigning each respondent to the right category accordingly.

@@

For our study, we employ a technique called multilevel regression with post-stratification (MRP). This approach involves creating a model based on a smaller data set, such as our survey data, and then extending the model's findings to a larger population.

```{r}
#| echo: false
#| message: false
#| warning: false
#run the regression model using glm.
# gender, age_groups, race, stateicp, education_level and hispanic are used to 
# predit whether a person will vote biden or not

model <- survey_model

# Assuming 'model' is your model object from rstanarm
library(broom.mixed)

coefficients <- broom.mixed::tidy(model, conf.int = TRUE)

# Assuming you have knitr and kableExtra already installed and loaded
library(knitr)
library(kableExtra)

knitr::kable(coefficients,
             caption = "Coefficients from the Model",
             digits = 2) %>%
  kableExtra::kable_styling(latex_options = "scale_down")
